---
title: "ISLR R Lab & Excersice Notebook"
output: html_notebook
---

# Chapter 3

## Lab Excercise:
```{r}
library (MASS)
library (ISLR)  
```

### 3.6.3 Multiple Linear Regression

```{r}
lm.fit=lm(medv~lstat+age,data=Boston)
summary(lm.fit)
```

* Short hand to specific all predictors
```{r}
lm.fit=lm(medv~.,data = Boston)
summary(lm.fit)
```

* Vif - Calculates variance-inflation and generalized variance-inflation factors for linear, generalized linear, and other models.
```{r}
install.packages("car")
library(car)

vif(lm.fit)
```
* Regression excluding this predictor
```{r}
lm.fit1=lm(medv~.-age, data=Boston)
summary(lm.fit1)
```

* Alternatively, the update() function can be used.
```{r}
lm.fit1=update(lm.fit, ~.-age)
```

### 3.6.4 Interaction Terms

* The syntax `lstat:black` tells R to include an interaction term between
lstat and black
* The syntax lstat*age simultaneously includes lstat, age, and the interaction term lstat×age as predictors; it is a shorthand for lstat+age+lstat:age.

```{r}
summary(lm(medv~lstat*age, data=Boston))
```

### 3.6.5 Non-linear Transformations of the Predictors

* I(X^2), to include non linear predictor

```{r}
lm.fitWithNLP=lm(medv~lstat+I(lstat^2), data=Boston)
summary(lm.fitWithNLP)
```
* use the *anova()* (analysis-of-variance) function to further quantify the extent to which the quadratic fit is superior to the linear fit
```{r}
lm.fit=lm(medv~lstat, data=Boston)
anova(lm.fit, lm.fitWithNLP)
par(mfrow=c(2,2))
plot(lm.fitWithNLP)
```
* *poly()* function to create the polynomial within lm()

```{r}
lm.fitWithPoly=lm(medv~poly(lstat, 5), data= Boston)
summary(lm.fitWithPoly)
```
* It is not limited to use only polynomial transformation, you can use other transformation like log

```{r}
summary(lm(medv~log(rm), data= Boston))
```

### 3.6.6 Qualitative Predictors

* The Carseats data includes qualitative predictors such as Shelveloc,
```{r}
summary(Carseats)
names(Carseats)
lm.fit=lm(Sales~.+Income:Advertising+Price:Age,data=Carseats)
summary(lm.fit)
```

* The contrasts() function returns the coding that R uses for the dummy variables.
```{r}
attach(Carseats)
?contrasts(ShelveLoc)
```

### 3.6.7 Writing Functions

```{r}
LoadLibraries=function (){
 library (ISLR)
 library (MASS)
 print (" The libraries have been loaded .")
}

LoadLibraries()
```





